Project Setup

### 2024-11-29 setup.qmd
Use global language and tidy _quarto.yml
Add Console notice

---
title: "Project Setup"
lang: en
engine: knitr
---

@@

```r
table_info <- c(
  title = "penguins dataset",
  description = "Size measurements for adult foraging penguins near Palmer Station, Antarctica"
)
descriptions <- c(
  species = "a character string denoting penguin species",
  island = "a character string denoting island in Palmer Archipelago, Antarctica",
  bill_length_mm = "a number denoting bill length (millimeters)",
  bill_depth_mm = "a number denoting bill depth (millimeters)",
  flipper_length_mm = "an integer denoting flipper length (millimeters)",
  body_mass_g = "an integer denoting body mass (grams)",
  sex = "a character string denoting penguin sex",
  year = "an integer denoting the study year"
)
vals <- list(
  species = c("Adelie", "Gentoo", "Chinstrap"),
  island = c("Torgersen", "Biscoe", "Dream"),
  sex = c("male", "female"),
  year = c(2007, 2008, 2009)
)
```

@@

```r
# Read data and create schema
dat_filename <- "Data.csv"
dat <- read.csv(dat_filename)
dat_schema <- frictionless::create_schema(dat)

>>>>

---
title: "Project Setup"
engine: knitr
---

@@

```{.r filename="Console"}
table_info <- c(
  title = "penguins dataset",
  description = "Size measurements for adult foraging penguins near Palmer Station, Antarctica"
)
descriptions <- c(
  species = "a character string denoting penguin species",
  island = "a character string denoting island in Palmer Archipelago, Antarctica",
  bill_length_mm = "a number denoting bill length (millimeters)",
  bill_depth_mm = "a number denoting bill depth (millimeters)",
  flipper_length_mm = "an integer denoting flipper length (millimeters)",
  body_mass_g = "an integer denoting body mass (grams)",
  sex = "a character string denoting penguin sex",
  year = "an integer denoting the study year"
)
vals <- list(
  species = c("Adelie", "Gentoo", "Chinstrap"),
  island = c("Torgersen", "Biscoe", "Dream"),
  sex = c("male", "female"),
  year = c(2007, 2008, 2009)
)
```

@@

```{.r filename="Console"}
# Read data and create schema
dat_filename <- "Data.csv"
dat <- read.csv(dat_filename)
dat_schema <- frictionless::create_schema(dat)
